The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
independently from to independent of

The current scientific data deluge, in which datasets grow faster in size and complexity than scientists can keep up with,
defines several new challenges for information systems. Scientists wish to 
discover new, unique, and significant patterns in datasets that explain biological 
phenomena not yet understood. The discovery of new patterns showing the 
causes and effects of various biological phenomena is often beyond the scope of single datasets.
For example, systems biologists integrate micro-array differential expression datasets to 
biological pathways, using various other datasets to provide evidence for the links~\cite{Staab2007}. 
Another prominent example is drug discovery, in which a new unique chemical entity is designed or discovered 
based on a description of its required biological properties. This process requires the effective 
linkage of many scientific datasets that are both sparse and are growing independently from each
other~\cite{Belleau2008,Samwald2011,Williams2012}.

>>>>

The current scientific data deluge, in which datasets grow faster in size and complexity than scientists can keep up with,
defines several new challenges for information systems. Scientists wish to 
discover new, unique, and significant patterns in datasets that explain biological 
phenomena not yet understood. The discovery of new patterns showing the 
causes and effects of various biological phenomena is often beyond the scope of single datasets.
For example, systems biologists integrate micro-array differential expression datasets to 
biological pathways, using various other datasets to provide evidence for the links~\cite{Staab2007}. 
Another prominent example is drug discovery, in which a new unique chemical entity is designed or discovered 
based on a description of its required biological properties. This process requires the effective 
linkage of many scientific datasets that are both sparse and are growing independent of each
other~\cite{Belleau2008,Samwald2011,Williams2012}.
